---
output: github_document
---

<!-- avoid border around images -->
<style>
    img {
        border-style: none;
        width: 80%;
    }
</style>

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cubethemes

<!-- badges: start -->
<!-- badges: end -->

{cubethemes} is designed to enable cubies to create great data visualisations that comply with the 
Cube Group Brand Guidelines.

## Installation

You can install the development version of {cubethemes} from github using devtools:

``` r
# install.packages("devtools")
devtools::install_github("zerogetsamgow/cubethemes")
```

## Usage

```{r setup, echo=FALSE}
library(ggplot2)
library(tidyverse,verbose = FALSE, warn.conflicts = FALSE)
library(stringr)
```

{cubethemes} is designed to produce {gglot2} that comply with the Cube Brand Guidelines simply. For example.

```{r white_example, warnings=FALSE}
library(cubethemes)
library(cubepalette)

## basic example code
ggplot2::ggplot(data=iris,aes(x=Sepal.Length, y = Petal.Length,colour=Species)) +
  geom_point(size=3) +
  scale_colour_manual(values=cube_palettes_discrete$dark,labels=stringr::str_to_title) +
  scale_x_continuous(name="Sepal length")+
  scale_y_continuous(name="Petal length")+
  theme_cube_white()
```

## Three themes to cubify them all  

{cubethemes} exports three themes - `theme_cube_white()`(seen above), `theme_cube_green()` and `theme_cube_orange` to enable plots to be produced for any Cube publication. 

Each of these themes is designed to work with different discrete palettes from {cubepallete}:

- `theme_cube_white()` with `cube_palette_discrete$dark`

- `theme_cube_green()` with `cube_palette_discrete$light`

```{r green example, warnings = FALSE}
## basic example of a green plot
ggplot(data=iris,aes(x=Sepal.Length, y = Petal.Length,colour=Species)) +
  geom_point(size=3) +
  scale_colour_manual(values=cube_palettes_discrete$light,labels=stringr::str_to_title) +
  scale_x_continuous(name="Sepal length")+
  scale_y_continuous(name="Petal length")+
  labs(title="Sepal and petal lengths of irises")+
  theme_cube_green()
```


- `theme_cube_orange()` with `cube_palette_discrete$other`

These themes can also work with the `cube_palette_tints` palettes `greys`,`greens` and `oranges`. 

```{r orange example, warnings=FALSE}
## basic example of a green plot
ggplot(data=mtcars,aes(x = as.factor(cyl), colour=NULL, fill=as.factor(cyl), group=cyl)) +
  geom_histogram(stat="count")+
  scale_fill_manual(name="Cylinders", values=cube_palettes_tints$greens,labels=stringr::str_to_title) +
  scale_y_continuous(name="Count", expand=c(0,0.04))+
  scale_x_discrete(name=NULL)+
  labs(title="Count of cylinders in mtcars")+
  theme_cube_orange()
```

As well as utilising the {cubepalette} these themes are rendered using {showtext} to allow the use of `Agenda` font. {cubetheme} installs these fonts.

## Maps for any background  

{cubethemes} exports a theme - `theme_cube_map()` to be used when plotting maps. This theme can be produced with white, green, orange or grey backgrounds. White is the default. Green and grey work with the default background colours in Cube's PowerPoint template.
```{r map_prep, echo=FALSE, warnings = FALSE}
library(sf)
library(strayr)
```


```{r map_grey, warnings = FALSE}

## basic example of a map with grey background
ggplot(
  data = 
    strayr::read_absmap(
      name="state2021",
      remove_year_suffix = TRUE
      ) |> 
    filter(state_name %in% strayr::state_name_au) |> 
    mutate(state_name = 
             factor(
               state_name, 
               levels=strayr::state_name_au)
           ),
  aes(fill=state_name, x=cent_long, y =cent_lat, label = str_wrap(state_name,10))) +
  geom_sf() +
  geom_text(family="Agenda",colour = cubepalette::cube.darkgreen, lineheight=.5)+
  scale_fill_manual(guide='none',values=colorspace::lighten(strayr::palette_state_name_2016,.7)) +
  labs(title="States and Territories of Australia")+
  theme_cube_map(base_colour = "grey", base_size = 10)
```

```{r map_green, warnings = FALSE}

## basic example of a map with grey background
ggplot(
  data = 
    strayr::read_absmap(
      name="state2021",
      remove_year_suffix = TRUE
      ) |> 
    filter(state_name %in% strayr::state_name_au) |> 
    mutate(state_name = 
             factor(
               state_name, 
               levels=strayr::state_name_au)
           ),
  aes(fill=state_name, x=cent_long, y =cent_lat, label = str_wrap(state_name,10))) +
  geom_sf() +
  geom_text(family="Agenda",colour = cubepalette::cube.grey, lineheight=.5)+
  scale_fill_manual(guide='none',values=colorspace::lighten(strayr::palette_state_name_2016,.2)) +
  labs(title="States and Territories of Australia")+
  theme_cube_map(base_colour = "green", base_size = 10)
```

