---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cubethemes

<!-- badges: start -->
<!-- badges: end -->

{cubethemes} is designed to enable cubies to create great data visualisations that comply with the 
Cube Group Brand Guidelines.

## Installation

You can install the development version of {cubethemes} from github using devtools:

``` r
# install.packages("devtools")
devtools::install_github("zerogetsamgow/cubethemes")
```

## Usage

{cubethemes} is designed to produce {gglot2} that comply with the Cube Brand Guidelines simply. For example.

```{r example}
library(ggplot2)
library(cubethemes)
library(cubepalette)
library(stringr)
## basic example code
ggplot(data=iris,aes(x=Sepal.Length, y = Petal.Length,colour=Species)) +
  geom_point(size=3) +
  scale_colour_manual(values=cube_palettes_discrete$dark,labels=stringr::str_to_title) +
  scale_x_continuous(name="Sepal length")+
  scale_y_continuous(name="Petal length")+
  theme_cube_white()
```

## Three themes to cubify them all  

{cubethemes} exports three themes - `theme_cube_white()`(seen above), `theme_cube_green()` and `theme_cube_pink` to enable plots to be produce any Cube publication. 

Each of these themes is designed to work with different discrete palettes from {cubepallete}:

- `theme_cube_white()` with `cube_palette_discrete$dark`

- `theme_cube_green()` with `cube_palette_discrete$light`

```{r example}
## basic example of a green plot
ggplot(data=iris,aes(x=Sepal.Length, y = Petal.Length,colour=Species)) +
  geom_point(size=3) +
  scale_colour_manual(values=cube_palettes_discrete$light,labels=stringr::str_to_title) +
  scale_x_continuous(name="Sepal length")+
  scale_y_continuous(name="Petal length")+
  labs(title="Comparison of sepal and petal of irises")+
  theme_cube_green()
```


- `theme_cube_pink()` with `cube_palette_discrete$other`

These themes can also work with the `cube_palette_tints` palettes `greys`,`greens` and `pinks`. 

```{r example}
## basic example of a green plot
ggplot(data=mtcars,aes(x = as.factor(cyl), colour=NULL, fill=as.factor(cyl), group=cyl)) +
  geom_histogram(stat="count",size=3)+
  scale_fill_manual(name="Cylinders", values=cube_palettes_tints$greens,labels=stringr::str_to_title) +
  scale_y_continuous(name="Count")+
  scale_x_discrete(name=NULL)+
  labs(title="Count of cylinders in mtcars dataset")+
  theme_cube_pink()
```

As well as utilising the {cubepalette} these themes are rendered using {showtext} to allow the use of `Agenda` font. {cubetheme} installs these fonts.
